---
title: "exploration"
output: html_document
date: "2023-12-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Packages, message = FALSE, warn = FALSE}
library(tidyverse)
library(terra)
source('code/src/calculate-texture.R')
source('code/src/color-space-transform.R')
source('code/src/meanshift-segmentation.R')
```

## Read in image

Read in the original image to generate features from. This image was taken on an iPhone and has 3 channels: red, green, and blue.

```{r Look at RGB image}
rgb_path <- 'clean_data/quadrats/quadrat34/rgb.tif'
rgb <- terra::rast(rgb_path)

plotRGB(rgb)
```

## Image segmentation

The first technique we perform is image segmentation using https://github.com/fjean/pymeanshift.

```{r}
rgb_segmented_path <- segment_image(rgb_path, spatial_radius = 6, range_radius = 4.5, min_density = 50)
rgb_segmented <- terra::rast(rgb_segmented_path)

plotRGB(rgb_segmented)
```

## Color space transformations

Images can be transformed into various color spaces such as HSV, LAB, YUV, which may help machine learning algorithms recogonize patterns.

```{r}
hsv_segmented_path <- color_transform(rgb_segmented_path, transform = 'RGBtoHSV')
hsv_segmented <- terra::rast(hsv_segmented_path) 

plotRGB(hsv_segmented)
```

## Texture calculation

Edges of objects can be recognized using texture measurements from the Gray Level Co-Occurence matrix.

```{r}
hsv_contrast_path <- calculate_texture(hsv_segmented_path, window = 5, statistic = "contrast", layer = 1L, do_computation = TRUE)
hsv_contrast <- terra::rast(hsv_contrast_path)

hsv_contrast
```
